Polynomial expansions of finite volume data in a cut cell context

### 2023-04-13 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
the footnote puts its foot in the door

Given a sufficiently smooth function $\psi$, we can approximate $\psi$
in the neighborhood of $\xbar$ using a Taylor expansion to order $P$:
\begin{equation}
\psi(\xbold)  =  \sum\limits_{p < P} C^p (\xbar - \xbar)^p \label{eqn::taylor}
\end{equation}
where $C^p$ this appropriate Taylor coefficient.  In three dimensions,
\begin{equation}
  C^p =\frac{1}{p!}
      \frac{\partial^{p_0}}{\partial x_0}
      \frac{\partial^{p_1}}{\partial x_1}
      \frac{\partial^{p_2}}{\partial x_2}  (\psi).
\end{equation}  
In finite volume  methods, we define grid data to be
averages over volumes.   So if we discretize the smooth function
$\psi$, the average over the volume $\ibold$ is given by
\begin{equation*}
 V_\ibold <\psi>_\ibold = \int\limits_{V_\ibold} \psi(\xbold) dV
\end{equation*}
If we insert the Taylor expansion \ref{eqn::taylor}, we get a discrete
approximation to the smooth function $\psi$ that is accurate to order $P$.
\begin{equation*}
 V_\ibold <\psi>_\ibold = \sum\limits_{p < P} C^p m^p. 
\end{equation*}
This forms a local polynomial expansion of $\psi$ around the volume
$\ibold$ expressed in terms moments ($m$) which are the natural
products of grid generation.  Modern, higher order embedded boundary
methods use this description directly to generate stencils
\cite{Overton2022a, Devendran2017, Schwartz2015}.  At the
core, all these algorithms have a similar procedure for finding the
Taylor coefficients $C^p$ which is worth discussing \footnotemark[7].

@@

\footnotetext[6] {The discerning reader will notice that this
  discussion assumes that the equation set used to create $C$ only
  includes the volume equations.   Devendran \cite{Devendran2017} also
  include boundary condition equations in the equation set.  For
  simple enough boundary conditions, this works very well.   There are
  many equation sets, however, which do not lend themselves easily to
  this approach.   Notably, hyperbolic equations often have boundary 
  conditions which are fomulated in terms of characteristic
  variables.    Using this information in the system of equations used
  to calculate Taylor coefficients is still a matter of research.}

>>>>

Given a sufficiently smooth function $\psi$, we can approximate $\psi$
in the neighborhood of $\xbar$ using a Taylor expansion to order $P$:
\begin{equation}
\psi(\xbold)  =  \sum\limits_{p < P} C^p (\xbar - \xbar)^p \label{eqn::taylor}
\end{equation}
where $C^p$ this appropriate Taylor coefficient.  In three dimensions,
\begin{equation}
  C^p =\frac{1}{p!}
      \frac{\partial^{p_0}}{\partial x_0}
      \frac{\partial^{p_1}}{\partial x_1}
      \frac{\partial^{p_2}}{\partial x_2}  (\psi).
\end{equation}  
In finite volume  methods, we define grid data to be
averages over volumes.   So if we discretize the smooth function
$\psi$, the average over the volume $\ibold$ is given by
\begin{equation*}
 V_\ibold <\psi>_\ibold = \int\limits_{V_\ibold} \psi(\xbold) dV
\end{equation*}
If we insert the Taylor expansion \ref{eqn::taylor}, we get a discrete
approximation to the smooth function $\psi$ that is accurate to order $P$.
\begin{equation*}
 V_\ibold <\psi>_\ibold = \sum\limits_{p < P} C^p m^p. 
\end{equation*}
This forms a local polynomial expansion of $\psi$ around the volume
$\ibold$ expressed in terms moments ($m$) which are the natural
products of grid generation.  Modern, higher order embedded boundary
methods use this description directly to generate stencils
\cite{Overton2022a, Devendran2017, Schwartz2015}.  At the
core, all these algorithms have a similar procedure for finding the
Taylor coefficients $C^p$ which is worth discussing

The discerning reader will notice that
the equation set used to create $C$ only includes the volume
equations.  Devendran \cite{Devendran2017} also include boundary
condition equations in the equation set.  For simple enough boundary
conditions, this works very well.  There are many equation sets,
however, which do not lend themselves easily to this approach.
Notably, hyperbolic equations often have boundary conditions which are
fomulated in terms of characteristic variables.  Using this
information in the system of equations for Taylor coefficients is
still a matter of research.  We therefore believe that restricting
ourselves to the volume equations can provide insight valuable to
developers of this class of algorithms.

@@

\footnotetext[7] {.}
